Supplementary Information

### 2021-06-03 doc/manuscript/ForestGEO_treerings_SI.Rmd
add urls for full results
#130

climwin_generic = "Rows correspond to the four different models run: (1) all RW data, (2) RW for the subset of cores for which $DBH could be reconstructed, (3) BAI, and (4)  AGB growth. The first four columns give statistics for seasonal windows tested in *climwin*, where window open and close indicate months prior to the last month in the climwin analysis window for the site (Table S1). Difference in $AIC$ relative to a model with no climate term (first column) is used to select the most influential seasonal window (second column). The third and fourth columns give values of linear and quadratic terms for each seasonal window. The final column shows the correlation of individual-level residuals to the selected climate driver, with the function fit in *climwin* (not the final fit)."

GLS_generic_legend = " for all three growth metrics examined here. For each species that met the criteria for inclusion in the analysis, relationships are plotted if included in top model. For each relationship shown, other terms in the model are held constant at their median. Best-fit polynomials are plotted with solid lines when both first- and second-order terms are significant (t-test’s p-value <0.05), dashed lines when only one term is significant, and dotted lines when neither is significant. Transparent ribbons indicate 95% confidence intervals. *Climwin*-selected climate drivers are coded on the x-axes as the climate variable name followed by the range of months (p=previous year, c=current year) over which it is most influential. Vertical grey lines indicate the long-term mean for the climate driver, shading indicates 1 SD."

@@

![`r GLS_BCNM_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/BCI.png){ width=90% }

@@

![`r GLS_SCBI_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/SCBI.png){ width=90% }

@@

![`r GLS_SCBI_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/SCBI_with_Year.png){ width=90% }

@@

![`r GLS_LT_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/NewMexico.png){ width=90% }

>>>>

climwin_generic = "Rows correspond to the four different models run: (1) all RW data, (2) RW for the subset of cores for which $DBH could be reconstructed, (3) BAI, and (4)  AGB growth. The first four columns give statistics for seasonal windows tested in *climwin*, where window open and close indicate months prior to the last month in the climwin analysis window for the site (Table S1). Difference in $AIC$ relative to a model with no climate term (first column) is used to select the most influential seasonal window (second column). The third and fourth columns give values of linear and quadratic terms for each seasonal window. The final column shows the correlation of individual-level residuals to the selected climate driver, with the function fit in *climwin* (not the final fit). Parallel figures for all sites may be found at https://github.com/EcoClimLab/ForestGEO-tree-rings/tree/master/doc/manuscript/tables_figures/SI_figures/climwin_plots_combined."

GLS_generic_legend = " for all three growth metrics examined here. For each species that met the criteria for inclusion in the analysis, relationships are plotted if included in top model. For each relationship shown, other terms in the model are held constant at their median. Best-fit polynomials are plotted with solid lines when both first- and second-order terms are significant (t-test’s p-value <0.05), dashed lines when only one term is significant, and dotted lines when neither is significant. Transparent ribbons indicate 95% confidence intervals. *Climwin*-selected climate drivers are coded on the x-axes as the climate variable name followed by the range of months (p=previous year, c=current year) over which it is most influential. Vertical grey lines indicate the long-term mean for the climate driver, shading indicates 1 SD. Parallel figures for all sites may be found at https://github.com/EcoClimLab/ForestGEO-tree-rings/tree/master/doc/manuscript/tables_figures/SI_figures/composite_plots."

@@

![`r GLS_BCNM_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/BCI.png){ width=85% }

@@

![`r GLS_SCBI_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/SCBI.png){ width=85% }

@@

![`r GLS_SCBI_year_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/SCBI_with_Year.png){ width=85% }

@@

![`r GLS_LT_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/NewMexico.png){ width=85% }
